The evolution of badges of status with learners

### 2019-09-06 QD_presentation.Rmd
done with QD presentation

@@

>>>>

## What parameters influence responsiveness?

### Distribution of quality

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Simulations//learHonest_//QualStDv_//compDistrNorm1Unif.png")
```

## What parameters influence responsiveness?

### Distribution of quality

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Simulations//learHonest_//QualStDv_//compDistrDiff.png")
```

## What parameters influence responsiveness?

### Strength of quality influence on competition outcome

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Simulations//learHonest_//strQual_//compStr1_last.png")
```

## What parameters influence responsiveness?

### Strength of quality influence on competition outcome

```{r,echo=FALSE,out.width='45%',fig.show='hold'}
knitr::include_graphics("Simulations//learHonest_//strQual_//compStrDiff.png")
knitr::include_graphics("Simulations//learHonest_//strQual_//compStrpDove.png")
```

# Why the hell is responsiveness so low?

@@

## Concluding

* Learning is good, even if you do not learn about your opponent. You still learn about you
* Learning reduces aggressive interactions
* Learning splits up individuals into _types_

### 2019-09-06 QD_presentation.tex
done with QD presentation

\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{cartoonRBF} \caption{\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.}\label{fig:fig2}
\end{figure}

>>>>

\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array}

@@

\begin{equation*}
  \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error}
\end{equation*}

\begin{figure}
\includegraphics[width=0.6\linewidth]{cartoonRBF} \caption{\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.}\label{fig:fig2}
\end{figure}

\hypertarget{our-model}{%
\section{Our model}\label{our-model}}

\begin{frame}{The hawk-dove game 2.0}
\protect\hypertarget{the-hawk-dove-game-2.0}{}

\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{1cm} | >{\centering\arraybackslash}p{4.5cm} | >{\centering\arraybackslash}p{4.5cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

\begin{equation*}
p_w=\frac{1}{1+e^{-\beta(Q_i-Q_j)}}
\end{equation*}

\begin{center}\includegraphics[width=0.5\linewidth]{QD_presentation_files/figure-beamer/unnamed-chunk-9-1} \end{center}

\begin{frame}{Sender Code}
\protect\hypertarget{sender-code}{}

\begin{equation*}
s_i = \frac{1}{1+e^{-(\epsilon_i+\gamma_iQ_i)}}
\label{eq:react_norm}
\end{equation*}

\begin{center}\includegraphics[width=0.5\linewidth]{QD_presentation_files/figure-beamer/unnamed-chunk-10-1} \end{center}

\begin{frame}{Receiver code}
\protect\hypertarget{receiver-code}{}

\begin{equation*}
  \Delta V_{t(s)}=\alpha (R_t-V_t)
\end{equation*}

\begin{center}\includegraphics[width=0.6\linewidth]{cartoonRBF} \end{center}

\hypertarget{results}{%
\section{Results}\label{results}}

\begin{frame}{When individuals do \emph{NOT} vary in quality}
\protect\hypertarget{when-individuals-do-not-vary-in-quality}{}

\begin{center}\includegraphics[width=0.8\linewidth]{Simulations//QualStDv_//hawkDoveLearn} \end{center}

\begin{frame}{When individuals \emph{DO} vary in quality}
\protect\hypertarget{when-individuals-do-vary-in-quality}{}

\begin{center}\includegraphics[width=0.8\linewidth]{Simulations//QualStDv_//hawkDoveLearn_1} \end{center}

\begin{frame}{Overal effect of quality variation}
\protect\hypertarget{overal-effect-of-quality-variation}{}

\begin{center}\includegraphics[width=0.8\linewidth]{Simulations//QualStDv_//effectQualVariance} \end{center}

\begin{frame}{How does variation among \emph{learners} look like?}
\protect\hypertarget{how-does-variation-among-learners-look-like}{}

\begin{center}\includegraphics[width=0.9\linewidth]{Simulations//QualStDv_//WeightsVarQualSt} \end{center}

\begin{frame}{How do the learning dynamics look like?}
\protect\hypertarget{how-do-the-learning-dynamics-look-like}{}

\includegraphics[width=0.8\linewidth]{Simulations//mutType_//learnDyn200}

\begin{frame}{How do learners behave when signals are honest?}
\protect\hypertarget{how-do-learners-behave-when-signals-are-honest}{}

\includegraphics[width=0.9\linewidth]{Simulations//learHonest_//QualStDv_//weightsVarQualSt}

\begin{frame}{What parameters influence responsiveness?}
\protect\hypertarget{what-parameters-influence-responsiveness}{}

\begin{block}{Distribution of quality}

\begin{center}\includegraphics[width=0.9\linewidth]{Simulations//learHonest_//QualStDv_//compDistrNorm1Unif} \end{center}

\begin{frame}{What parameters influence responsiveness?}
\protect\hypertarget{what-parameters-influence-responsiveness-1}{}

\begin{block}{Distribution of quality}

\begin{center}\includegraphics[width=0.9\linewidth]{Simulations//learHonest_//QualStDv_//compDistrDiff} \end{center}

\begin{frame}{What parameters influence responsiveness?}
\protect\hypertarget{what-parameters-influence-responsiveness-2}{}

\begin{block}{Strength of quality influence on competition outcome}

\begin{center}\includegraphics[width=0.9\linewidth]{Simulations//learHonest_//strQual_//compStr1_last} \end{center}

\begin{frame}{What parameters influence responsiveness?}
\protect\hypertarget{what-parameters-influence-responsiveness-3}{}

\begin{block}{Strength of quality influence on competition outcome}

\includegraphics[width=0.45\linewidth]{Simulations//learHonest_//strQual_//compStrDiff}
\includegraphics[width=0.45\linewidth]{Simulations//learHonest_//strQual_//compStrpDove}

\hypertarget{why-the-hell-is-responsiveness-so-low}{%
\section{Why the hell is responsiveness so
low?}\label{why-the-hell-is-responsiveness-so-low}}

\begin{frame}{How do learners fare against pure strategies?}
\protect\hypertarget{how-do-learners-fare-against-pure-strategies}{}

\begin{center}\includegraphics[width=0.8\linewidth]{Simulations//mutType_//evolDynTypes} \end{center}

\begin{frame}{Concluding}
\protect\hypertarget{concluding}{}

\begin{itemize}
\tightlist
\item
  Learning is good, even if you do not learn about your opponent. You
  still learn about you
\item
  Learning reduces aggressive interactions
\item
  Learning splits up individuals into \emph{types}
\end{itemize}

\begin{frame}{What's next?}
\protect\hypertarget{whats-next}{}

\begin{itemize}
\tightlist
\item
  Let reaction norm evolve, under different initial conditions.
\item
  Let learning parmeters evolve
\item
  Let the communication system co-evolve
\end{itemize}
